---
title: "Central Limit Theory App"
subtitle: "a Coursera 'Developing Data Products' Project"
author: "Brian Yi Liu"
date: "April 14, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Overview

A web app that provides a demonstration of the effect of Central Limit Theorem (CLT) on simulated samples of different distributions has been built with Shiny

You can access the application [here](https://yliu777.shinyapps.io/CentralLimitTheorem/)

The raw code for the application is hosted on Github [here](https://github.com/yliu777/Data_Product_project)

## App Features
- Choose from four distributions with customizable parameter
    + Normal, Uniform, Log-Normal, Exponential
- Choose total number of the samples generated
- Choose sample size
- Compare sample distribution with normal distribution
- Compare sample mean and standard deviation with its expected value


## Central Limit Theory
Central Limit Theorem states that the sampling distribution of the sampling mean approaches a normal distribution as the sample size gets larger, no matter what the shape of the population distribution

Watch the lecture on Central Limit Theory [here](https://www.youtube.com/watch?v=FAIyVHmniK0&feature=youtu.be&list=PLpl-gQkQivXiBmGyzLrUjzsblmQsLtkzJ)

See [wikipedia](https://en.wikipedia.org/wiki/Central_limit_theorem) for a detailed explanation on Central Limit Theory

## Demonstration
Here is a demonstration of central limit theory comparing a 1000 samples of size 1 and 40 with exponential distribution

```{r, message = FALSE, echo=FALSE, cache=TRUE, warning=FALSE}
library(ggplot2)
lambda=0.2; n=40
mns=NULL
for (i in 1:1000) mns=c(mns,mean(rexp(n,lambda)))
dist <- data.frame(
  x = c(rexp(1000,lambda),mns),
  size = factor(rep(c(1,40), rep(1000, 2))))
g <- ggplot(dist, aes(x = x, fill = size)) + geom_histogram(binwidth=0.3, 
                                                            colour = "black", 
                                                            aes(y = ..density..)) 
g <- g + stat_function(fun = dnorm,args=list(mean=(1/lambda),sd=(1/lambda/sqrt(40))))
g + facet_grid(. ~ size) +xlim(0,20)
```
